The state of knowledge for marine invertebrate biodiversity in the continental US

### 2017-06-15 manuscript.Rmd
[fix #26] add FWRI mention in discussion

Species that are included in the list but do not have records in databases could be (1) rare: they have never been collected or have been collected only a few times, and the corresponding records have not been digitized yet; (2) difficult to preserve: large, very small, or fragile species are preserved less frequently; (3) are in the database under a different name: the species has been synonimized or re-identified since the publication of the list under a different name that may be included in the database; (4) at the limit of its range: it was included in the list because it is known to occur at the limit of its geographic zone, but has never been collected within the boundaries; (5) does not have geographic coordinates associated with it: it can be in the database but without georeferenced datapoints that made it possible to discover them.

@@

Museum specimens are critical to validate the occurrence of species [@Rocha2014], especially for marine invertebrates for which species limits based on morphology have been known to be challenged by other lines of evidence including molecular data [@Knowlton2000]. Some of the discrepancies observed between the number of species for which occurrence data and museum specimens are available suggest that additional digitization of collections (including capturing their geographic information) are needed.

>>>>

Species that are included in the list but do not have records in databases could be (1) rare: they have never been collected or have been collected only a few times, and the corresponding records have not been digitized yet; (2) difficult to preserve: large, very small, or fragile species are preserved less frequently; (3) are in the database under a different name: the species has been synonimized or re-identified since the publication of the list under a different name that may be included in the database; (4) at the limit of its range: it was included in the list because it is known to occur at the limit of its geographic zone, but has never been collected within the boundaries; (5) does not have geographic coordinates associated with it: it can be in the database but without georeferenced datapoints that made it possible to discover them. By querying iDigBio we found that for the `r format(not_really_in_database$idig_gom_n_spp_not_in_db, big.mark=",")` species that do not appear within the geographic range of the Gulf of Mexico but are on the list, `r format_output(not_really_in_database$idig_gom_p_spp_not_in_db*100)`% are truly absent from iDigBio, while for the `r format(not_really_in_database$idig_gom_n_spp_no_coords, big.mark=",")` species that appear in iDigBio `r format_output(not_really_in_database$idig_gom_p_spp_no_coords*100)`%  do not have geographic coordinates associated with them, and for the ones that dok `r format_output(not_really_in_database$idig_gom_p_spp_within_usa*100)`% fall within the US waters (n = `r format(not_really_in_database$idig_gom_n_spp_within_usa, big.mark=",")`).

@@

Museum specimens are critical to validate the occurrence of species [@Rocha2014], especially for marine invertebrates for which species limits based on morphology have been known to be challenged by other lines of evidence including molecular data [@Knowlton2000]. Some of the discrepancies observed between the number of species for which occurrence data and museum specimens are available suggest that additional digitization of collections (including capturing their geographic information) are needed. For instance, one can expect that the digitization coverage for the Gulf of Mexico will greatly increase when records from the Florida Wildlife Research Institute collection (St Petersburg, FL) become integrated into the biodiversity information systems.
